---
title: "Wei-data_quality_review"
author: "Wei-Chun Lin"
date: "10/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(dplyr)
library(skimr)
library(foreign)
# Attaching benford analysis tool
library(benford.analysis)
library(moments)
library(ggplot2)
```

```{r}
finalProject <- read.spss("~/Desktop/R-bootcamp/Math630/data/PPD.sav", to.data.frame=TRUE)
```
#### 31. Data have been manually edited <br />

I do not find any suspicious sign.

#### 32, 33 Inflation skews the data or Natural/seasonal variation skews the data <br />

Using "skim" function to get all histograms and figure out several skewness data.
```{r}
# Using skim, we can get histograms of all variables. 
skim(finalProject)
```

Obvious skewness histograms: <br />
ANSIEDADFOBICA1 
ANSIEDADFOBICA3
Cortisol1
Cortisol2
Cortisol2
DEPRESIÓN2
EPDS
IDEACIÓNPARANOIDE3
OBSESIONESYCOMPULSIONES3
PSICOTICISMO1
PSICOTICISMO3

```{r}
# Remove empty row
finalProject <- finalProject[-c(45:73), ]

ggplot(finalProject, aes(x = Cortisol1))+
  geom_density()

skewness(finalProject$Cortisol1)

ggplot(finalProject, aes(x = Cortisol2))+
  geom_density()

skewness(finalProject$Cortisol2)

ggplot(finalProject, aes(x = Cortisol3))+
  geom_density()

skewness(finalProject$Cortisol3)

ggplot(finalProject, aes(x = ANSIEDADFOBICA1))+
  geom_density()

skewness(finalProject$ANSIEDADFOBICA1)

ggplot(finalProject, aes(x = ANSIEDADFOBICA3))+
  geom_density()

skewness(finalProject$ANSIEDADFOBICA3)

ggplot(finalProject, aes(x = DEPRESIÓN2))+
  geom_density()

skewness(finalProject$DEPRESIÓN2)

ggplot(finalProject, aes(x = EPDS))+
  geom_density()

skewness(finalProject$EPDS)

ggplot(finalProject, aes(x = IDEACIÓNPARANOIDE3))+
  geom_density()

skewness(finalProject$IDEACIÓNPARANOIDE3)

ggplot(finalProject, aes(x = OBSESIONESYCOMPULSIONES3))+
  geom_density()

skewness(finalProject$OBSESIONESYCOMPULSIONES3)

ggplot(finalProject, aes(x = PSICOTICISMO1))+
  geom_density()

skewness(finalProject$PSICOTICISMO1)

ggplot(finalProject, aes(x = PSICOTICISMO3))+
  geom_density()

skewness(finalProject$PSICOTICISMO3)
```
<br />

#### 34. Timeframe has been manipulated <br />
No sign of this kind of manipulation

#### 35. Frame of reference has been manipulated <br />
No sign of this kind of manipulation

#### 36. Author is untrustworthy <br />
No information to make the judgement.

#### 37. Collection process is opaque <br />
Data collection process is clear.

#### 38. Data assert unrealistic precision <br/>
The R-squart of prediction model is reasonable.

#### 39. There are inexplicable outliers <br/>
No

#### 40. An index masks underlying variation <br/>
Not found

#### 41. Results have been p-hacked <br/>
I haven't find p-hacked situation.

#### 42. Benford's Law fails

If the data follows Benford's Law, the numbers should be close to: <br />
Statistic	Value <br />
Mean	0.5 <br />
Variance	1/12 (0.08333…) <br />
Ex. Kurtosis	-1.2 <br />
Skewness	0 <br />

Here are several variables fails to Benford's law

```{r}

#Test skewness variables with benford function
benford(finalProject$ANSIEDADFOBICA1)

benford(finalProject$ANSIEDADFOBICA3)

benford(finalProject$IDEACIÓNPARANOIDE3)

benford(finalProject$PSICOTICISMO1)

```

#### 43. Too good to be true <br />
The result is reasonable.

#### 44. Data are aggregated to the wrong categories or geographies <br />
All variable names were stored as Spanish, we might need to translate to English.

#### 45. Data are in scanned documents <br />
No 



